%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Edson }{Contreras}
       {pc \& embedded software engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    \href{mailto:edrecon@gmail.com}{edrecon@gmail.com}
    \href{https://github.com/zxnord}{github/zxnord}
    \href{https://bitbucket.org/zxnord}{bitbucket/zxnord}
    +56994663278
    +56228413780
    ~
    Ruben Veloso 861
    8081709
    San Bernardo
    Chile
  \section{languages}
    Native Spanish
    Fluid English
    TOEIC:
    Listening [475 / 495]
    Reading [385 / 495]
    Speaking [170 / 200]
    Writing [190 / 200]
  \section{programming}
    Qt Framework
    (Qt4 and Qt5), VTK
    (VTK 7.1.1), C++
    (C++14), C, Java,
    Spring-boot, Python,
    Verilog
  \section{technologies}
    Linux, Docker,
    Kubernetes, Virtualization,
    Jenkins, Git, Perforce
  \section{embedded}
    MSP430, RaspberryPI
    FPGA, PIC
  \section{certificates}
    \href{http://bcert.me/scsokmjer}{Spring Core 5}
\end{aside}

\section{interests}

Desktop applications development, libraries development, embedded and hardware programming,
mobile applications, games development, visualization \& OpenGL

\section{education}

\begin{entrylist}
  \entry
    {2010–2013}
    {Sciences of Electronics Engineering}
    {Federico Santa Maria University, Chile}
    {Achieved Electronics specialization in unix \& embedded programming}
  \entry
    {2005–2010}
    {Sciences of Engineering}
    {Federico Santa Maria University, Chile}
    {Achieved B.Sc. Chilean degree equivalent majoring in embedded programming
}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2017 –}
    {BCI Bank Inc., Chile}
    {Software Engineer Lead}
    {Architect, designer and senior developer of Spring Boot based microservices on Kubernetes platform}
  \entry
    {2015 – 2017}
    {Synopsys Inc., Chile}
    {R\&D Sr I Software Engineer}
    {New hires interviewer and world wide presentor of new features for Sentaurus Visual}
  \entry
    {2015 – 2017}
    {Synopsys Inc., Chile}
    {R\&D II Software Engineer}
    {Features implementer, bug fixer and main developer of Sentaurus Visual}
  \entry
    {2013 – 2015}
    {Synopsys Inc., Chile}
    {R\&D I Software Engineer}
    {Bug fixer and tests developer for Sentaurus Visual}
%  \entry
%    {01/12 – 03/12}
%    {Synopsys Inc., Chile}
%    {Research Internship}
%    {TCL command testing and software regression tests design}
%  \entry
%    {2010 – 2012}
%    {Federico Santa Maria University}
%    {Part-time teacher}
%    {Matlab and Scilab teacher}
%  \entry
%    {2011 – 2012}
%    {Federico Santa Maria University}
%    {Teacher Assistant}
%    {FPGA and MSP430 University Lab Assistant}
%  \entry
%    {01/11 – 03/11}
%    {Egolucion Inc., Chile}
%    {Summer job}
%    {Optical multitouch software development for pattern recognition in walls and floors}
%  \entry
%    {2010 – 2011}
%    {Federico Santa Maria University}
%    {Part-time teacher}
%    {Matlab and Scilab usage}
\end{entrylist}

\newpage

\section{applications}

\begin{entrylist}
  \entry
    {2018 – }
    {Micro-services senior developer}
    {BCI Bank Inc., Chile}
    {Mantainer of OAuth2 internal enterprise login solution with Spring Security and MS Active Directory. Developed a  microservice for creating template-based protected excel documents.}
    \entry
    {2017 – }
    {Micro-services architect}
    {BCI Bank Inc., Chile}
    {Microservices design lead. Worked in Credit Cards payments and credits. Redisign of Wholesale banking web platform. Used Spring-boot on IBM Bluemix Kubernetes environment}
  \entry
    {2016 – 2017}
    {Sentaurus Visual}
    {Synopsys Inc., Chile}
    {Studied and removed legacy memory leaks (most of them) and prepared a presentation of good practices of memory management and use of C++11 smart pointers}
  \entry
    {2015 – 2016}
    {Sentaurus Visual}
    {Synopsys Inc., Chile}
    {Studied, Analyzed and implemented a major rework of the entire application in order to use newer Mesa version and C++ standard}
  \entry
    {2014 – 2015}
    {Sentaurus Visual}
    {Synopsys Inc., Chile}
    {Redesigned the rendering core in order to improve the performance rendering thousands of spheres in screen with VTK}
  \entry
    {2013 – 2014}
    {Sentaurus Visual}
    {Synopsys Inc., Chile}
    {Improved calculus of Stream traces in Vectorial field by applying multi-thread portable concepts with Qt framework}
  \entry
    {2012}
    {DSP I2C/USB data extractor}
    {University thesys}
    {An I2C/USB interface for extracting data from a DSP using a MSP430 with a Qt desktop application as frontend}
%  \entry
%    {2012}
%    {Spinbikenergy}
%    {University research}
%    {PyGTK user interface for control an electricity generator based on a static bicycle (spinning gym bicycle)}
\end{entrylist}

\section{achievements}

\begin{entrylist}
%   \entry
%    {2010}
%    {Spinbikenergy}
%    {University research.}
%    {As research group we won FDI government funds for innovation.}
  \entry
    {2019}
    {Bci Bank Inc., Chile}
    {Recognition award.}
    {Recognition for skills and team performance and invited to OSCON 2019.}
    \entry
    {2018}
    {Bci Bank Inc., Chile}
    {Recognition award.}
    {Recognition for develop the first project of payment through a Facebook Bot in Chile.}
  \entry
    {2016}
    {Synopsys Inc., Chile}
    {Recognition award.}
    {Awarded recognition for significant contribution to the company during year 06/2015 - 06/2016.}
  \entry
    {2011}
    {Spinbikenergy}
    {University research.}
    {3rd place in Chilectra's IEEE innovation contest.}
\end{entrylist}

\end{document}
